Continuous time

### 2023-09-25 continuous-time.qmd
subset data

## Data
Load the data and remove observations that occurred more than 3 hours into a session.
```{r}
#| label: load-data
dat <- read_rds("data/data-raw.rds")
if (!is.na(N_SUBSET)) {
  pid_subset <- sample(unique(dat$pid), N_SUBSET)
  dat <- filter(dat, pid %in% pid_subset)
}
dat <- dat |>
  mutate(
    duration = duration - duration[1],
    hours = duration / 60,
    .by = c(pid, session)
  ) |>
  mutate(
    ps = interaction(pid, session, sep = "_")
  ) |>
  filter(prompt == "Wellbeing")

dat <- dat |>
  filter(
    !is.na(mood),
    hours <= 3
  ) |>
  mutate(
    cl = case_when(
      mood == 0 ~ "left",
      mood == 1 ~ "right",
      TRUE ~ "none"
    ),
    mood100 = mood * 100
  )
```

@@

```{r}
#| label: lmer-pre-interaction
#| code-fold: show
dat_pre <- dat |>
  filter(
    # Session has a wellbeing measure at time = 0
    duration[1] == 0,
    .by = c(pid, session)
  ) |>
  mutate(
    pre = mood100[1],
    .by = c(pid, session)
  ) |>
  filter(
    hours != 0
  )

@@

```{r}
#| label: brms-cens
set.seed(345345)
tmp <- filter(
  dat,
  pid %in% sample(unique(pid), n_pids_sample)
)

@@

If we plot the fitted spline from both models, we in @fig-cens-compare that the shape is almost identical but the censored model is shifted upwards.

@@

Lastly, we'll also fit the interaction model using a censored normal distribution, again with `r n_pids_sample` participants.

```{r}
#| label: cens-pre-interaction
set.seed(5454545)
tmp_pre <- filter(dat_pre, pid %in% sample(unique(pid), n_pids_sample))

>>>>

## Data
Load the data and remove observations that occurred more than 3 hours into a session.
```{r}
#| label: load-data
dat <- read_rds("data/data-raw.rds")
dat <- dat |>
  mutate(
    duration = duration - duration[1],
    hours = duration / 60,
    .by = c(pid, session)
  ) |>
  mutate(
    ps = interaction(pid, session, sep = "_")
  ) |>
  filter(prompt == "Wellbeing")

dat <- dat |>
  filter(
    !is.na(mood),
    hours <= 3
  ) |>
  mutate(
    cl = case_when(
      mood == 0 ~ "left",
      mood == 1 ~ "right",
      TRUE ~ "none"
    ),
    mood100 = mood * 100
  )
if (!is.na(N_SUBSET)) {
  pid_subset <- sample(unique(dat$pid), N_SUBSET)
  dat <- filter(dat, pid %in% pid_subset) |> 
    droplevels()
}
```

@@

```{r}
#| label: lmer-pre-interaction
#| code-fold: show
dat_pre <- dat |>
  filter(
    # Session has a wellbeing measure at time = 0
    duration[1] == 0,
    .by = c(pid, session)
  ) |>
  mutate(
    pre = mood100[1],
    .by = c(pid, session)
  ) |>
  filter(
    hours != 0
  ) |> 
  droplevels()

@@

```{r}
#| label: brms-cens
#| results: hide
set.seed(345345)
tmp <- filter(
  dat,
  pid %in% sample(unique(pid), n_pids_sample)
)

@@

If we plot the fitted spline from both models, we see in @fig-cens-compare that the shape is almost identical but the censored model is shifted upwards.

@@

Lastly, we'll also fit the interaction model using a censored normal distribution, with `r min(n_pids_sample, nlevels(dat_pre$pid))` participants.

```{r}
#| label: cens-pre-interaction
#| results: hide
set.seed(5454545)
tmp_pre <- filter(
    dat_pre,
    pid %in% sample(
        unique(pid),
        # avoid taking sample larger than population 
        min(
            n_pids_sample,
            nlevels(pid)
        )
    )
)
